---
title: "How does the size affect fuel economy?"
execute:
  echo: false
  warning: false
---
```{r}
#| echo: false
#| warning: false

# importing all libraries, below
library(tidyverse)
library(primer.data)
library(rstanarm)

# Right here, I am assigning reading the input from "Automobile.csv" and assigning it to cars, which I have created.
cars <- read_csv(file = "Automobile.csv", show_col_types = FALSE)

# Making the ggplot. I want to see the correlation between displacement and mpg, so I set x = displacement and y = mpg. B/c mpg is dependent on x, so it is on the y axis.
cars_graph <- cars |> ggplot(aes(x = displacement, y = mpg)) + geom_point(mapping = aes(color = mpg)) + labs(title = "The Effect of Engine Displacement on Gas Mileage",
       x = "Engine Displacement",
       y = "Miles Per Gallon",
       subtitle = "Generally, as engine displacement increases,
       gas mileage decreases",
       caption = "Kaggle: Car Information Dataset") + theme_classic() + geom_smooth(method = "lm")
# Add a theme_classic makes it more organized


cars_graph
# displaying the plot

```
## Analysis
The displacement of an engine has a considerable effect on fuel economy. The data is from the Car Information Dataset found on Kaggle. Engine displacement is the amount of air the engine can combust. A 5.7L can hold and ignite that much air in the cylinders combined. Not suprisingly, higher displacement engines have a worse fuel economy because they burn more fuel. A higher displacement engine has 4x less fuel efficiency than a lower displacement engine.

```{r}



```

